### 2021-01-31 博士/毕业论文/ucasthesis/Tex/Chap_attack.tex
新增 attack 一章英文版

%%%% ijcai21-multiauthor.tex

\typeout{IJCAI--21 Multiple authors example}

% These are the instructions for authors for IJCAI-21.

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai21.sty is NOT the same than previous years'
\usepackage{ijcai21}

% Use the postscript times font!
\usepackage{times}
\renewcommand*\ttdefault{txtt}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\urlstyle{same}

%START: added by zhbli
\usepackage{subfigure}  % show sub-figure
\usepackage{algorithm}  % for algrithm
\usepackage{algorithmic}  % for algrithm
\usepackage{multirow}  % for multirow command used in the table
\usepackage{amsfonts}  % for mathbb
\usepackage{color,xcolor}  % 用于改变字体颜色
\usepackage{amssymb}  % 用于打对号
\usepackage{amsfonts}  % 用于 mathbb
%\usepackage{cite}  % 用于引用多篇文献
\newcommand{\eg}{e.g.}
\newcommand{\ie}{i.e.}
%\usepackage{float}  % 如果你确实需要把图片放在当前位置，不容改变，可以用float宏包的[H]选项。
%\usepackage[section]{placeins}  % 如果希望避免浮动体跨过 \section，可以使用 placeins 宏包。
%END: added by zhibi

% the following package is optional:
%\usepackage{latexsym}

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.

\title{Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking}

\iffalse
\author{
Zhenbang Li$^1$\and
Jin Gao$^2$\footnote{Corresponding Author}\and
YaYa Shi$^{2,3}$\and
Bing Li$^4$\and
Pengpeng Liang$^5$\And
Weiming Hu$^6$\\
\affiliations
$^1$First Affiliation\\
$^2$Second Affiliation\\
$^3$Third Affiliation\\
$^4$Fourth Affiliation\\
\emails
\{first, second\}@example.com,
third@other.example.com,
fourth@example.com
}
\else
\author{PaperID: 2266}
\fi

\begin{document}

\maketitle

\begin{abstract}

Siamese trackers are shown to be vulnerable to adversarial attacks recently. However, the existing attack methods craft the perturbations for each video independently, which comes at a non-negligible computational cost. The question is what if we can not get access to the limited computational resources in the real-world online-tracking phase.

@@

\end{abstract}

@@

\begin{figure}[htbp]
\centering
%\subfigure{\includegraphics[width=0.2\textwidth]{images/x.jpg}} \qquad
%\subfigure{\includegraphics[width=0.2\textwidth]{images/z.jpg}}
\includegraphics[width=0.45\textwidth]{images/1_v8.pdf}
\caption{An illustration of our attacks to SiamFC++ on some example tracking sequences from GOT-10k benchmark. Our approach generates the video-agnostic perturbations which can force SiamFC++ to follow a complicated trajectory at virtually no cost. This is realized by off-line training the perturbations so that the tracker mistakenly believes the \textit{fake target} area contains the object to be tracked (see the left heatmap). Moreover, the quality assessment branch in SiamFC++ is also misled to confirm this result (see the right heatmap). The \textit{fake target} size is gradually decreased.} 
%Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations. 
%Red represents the ground-truth bounding box, and green represents the predicted bounding box by the tracker.
%The purple dashed box marks the universal adversarial patch. The left heatmap represents the probability of each spatial position to contain the \textit{fake target}, and the right heatmap represents the target state estimation quality.}
\label{fig:1}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{images/network_v5.pdf}
\caption{The training pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the \textit{fake target} $p$ into $\textbf x$, the tracker outputs the location and size of the \textit{fake target} instead of the real target.}
\label{fig:net}
\end{figure}

@@

\begin{algorithm}[tb]
\caption{Training Process}
\label{alg:algorithm}
\textbf{Input}: Training dataset $\mathcal{V}$, Siamese tracker $\phi$, and max iteration number $N$.\\
\textbf{Output}: Imperceptible perturbation $\delta$, and adversarial patch $p$.
\begin{algorithmic}[1] %[1] enables line numbers
\STATE Let $k = 0$.
\WHILE{$k < N$}
\STATE Randomly pick a video $V\in \mathcal{V}$. The corresponding ground truth is $B^{gt}=\{b^{gt}_i\}^T_1$.
\STATE Randomly pick paired frames $I_t, I_s$ from $V$.
\STATE Generate template image $\textbf{z}$ according to $I_t$ and $b^{gt}_t$.
\STATE $\tilde{\textbf{z}} = \textbf{z} + \delta_k.$
\STATE Generate search image $\textbf{x}$ according to $I_s$ and $b^{gt}_s$.
\STATE Calculate the \textit{fake target} position $\{l^x, l^y, w, h\}$ with respect to the search image.
\STATE $\tilde{\textbf x} = A(\textbf x, p_k, (l^x, l^y), (w, h)).$
\STATE $\textbf{C, R, Q} = \phi(\tilde {\textbf x}, \tilde{\textbf z}).$
\STATE Generate fake labels $\textbf{C}^*,\textbf{R}^*,\textbf{Q}^*$ using $\{l^x, l^y, w, h\}$.
\STATE Calculate loss $L(\textbf{C, R, Q}, \textbf{C}^*, \textbf{R}^*, \textbf{Q}^*)$ using Equ. \ref{eq:loss}.
\STATE $\delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L).$
\STATE $p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L).$
\STATE $k = k + 1.$
\ENDWHILE
\STATE \textbf{return} $\delta_N, p_N.$
\end{algorithmic}
\label{alg}
\end{algorithm}

\begin{figure*}[t]
\centering
\includegraphics[width=0.95\textwidth]{images/vis_v4.pdf}
\caption{Our targeted attack results following a predefined \textit{fake trajectory} (indicated by the yellow targeted bounding box).}
\label{fig:vis}
\end{figure*}

@@

\clearpage
\bibliographystyle{named}
\bibliography{ijcai21}

\end{document}

>>>>

\chapter{Video-Agnostic Perturbations: Efficient Targeted Attacks for Siamese Visual Tracking} \label{chap:attack}

\section{Abstract}
Siamese trackers are shown to be vulnerable to adversarial attacks recently. However, the existing attack methods craft the perturbations for each video independently, which comes at a non-negligible computational cost. The question is what if we can not get access to the limited computational resources in the real-world online-tracking phase.

@@

@@

\begin{figure}[htbp]
\centering
%\subfigure{\includegraphics[width=0.2\textwidth]{Img/attack/x.jpg}} \qquad
%\subfigure{\includegraphics[width=0.2\textwidth]{Img/attack/z.jpg}}
\includegraphics[width=0.45\textwidth]{Img/attack/1_v8.pdf}
\caption{An illustration of our attacks to SiamFC++ on some example tracking sequences from GOT-10k benchmark. Our approach generates the video-agnostic perturbations which can force SiamFC++ to follow a complicated trajectory at virtually no cost. This is realized by off-line training the perturbations so that the tracker mistakenly believes the \textit{fake target} area contains the object to be tracked (see the left heatmap). Moreover, the quality assessment branch in SiamFC++ is also misled to confirm this result (see the right heatmap). The \textit{fake target} size is gradually decreased.} 
%Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations. 
%Red represents the ground-truth bounding box, and green represents the predicted bounding box by the tracker.
%The purple dashed box marks the universal adversarial patch. The left heatmap represents the probability of each spatial position to contain the \textit{fake target}, and the right heatmap represents the target state estimation quality.}
\label{fig:1}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{Img/attack/network_v5.pdf}
\caption{The training pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the \textit{fake target} $p$ into $\textbf x$, the tracker outputs the location and size of the \textit{fake target} instead of the real target.}
\label{fig:net}
\end{figure}

@@

\iffalse
\begin{algorithm}[tb]
\caption{Training Process}
\label{alg:algorithm}
\textbf{Input}: Training dataset $\mathcal{V}$, Siamese tracker $\phi$, and max iteration number $N$.\\
\textbf{Output}: Imperceptible perturbation $\delta$, and adversarial patch $p$.
\begin{algorithmic}[1] %[1] enables line numbers
\STATE Let $k = 0$.
\WHILE{$k < N$}
\STATE Randomly pick a video $V\in \mathcal{V}$. The corresponding ground truth is $B^{gt}=\{b^{gt}_i\}^T_1$.
\STATE Randomly pick paired frames $I_t, I_s$ from $V$.
\STATE Generate template image $\textbf{z}$ according to $I_t$ and $b^{gt}_t$.
\STATE $\tilde{\textbf{z}} = \textbf{z} + \delta_k.$
\STATE Generate search image $\textbf{x}$ according to $I_s$ and $b^{gt}_s$.
\STATE Calculate the \textit{fake target} position $\{l^x, l^y, w, h\}$ with respect to the search image.
\STATE $\tilde{\textbf x} = A(\textbf x, p_k, (l^x, l^y), (w, h)).$
\STATE $\textbf{C, R, Q} = \phi(\tilde {\textbf x}, \tilde{\textbf z}).$
\STATE Generate fake labels $\textbf{C}^*,\textbf{R}^*,\textbf{Q}^*$ using $\{l^x, l^y, w, h\}$.
\STATE Calculate loss $L(\textbf{C, R, Q}, \textbf{C}^*, \textbf{R}^*, \textbf{Q}^*)$ using Equ. \ref{eq:loss}.
\STATE $\delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L).$
\STATE $p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L).$
\STATE $k = k + 1.$
\ENDWHILE
\STATE \textbf{return} $\delta_N, p_N.$
\end{algorithmic}
\label{alg}
\end{algorithm}
\fi

\begin{figure*}[t]
\centering
\includegraphics[width=0.95\textwidth]{Img/attack/vis_v4.pdf}
\caption{Our targeted attack results following a predefined \textit{fake trajectory} (indicated by the yellow targeted bounding box).}
\label{fig:vis}
\end{figure*}

@@
